Daily Shelter and Overnight Services Availabilities

### 2024-09-26 paper/paper.qmd
cleaned data further and added some tests for data validty
minor edits + added basic histogram

```{r}
#| label: fig-marriages
#| fig-cap: Number of Marriages From 2018-2023
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) + 
  geom_point()
```

@@

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

@@

@@

# Model details {#sec-model-details}

## Posterior predictive check

## Diagnostics

>>>>

```{r}
#| label: fig-occupancyrate-vs-month
#| fig-cap: Shelter Occupancy Rate in 2024 Over the Months
#| echo: false

#data |> 
#  ggplot(aes(x = date, y = occupancy_rate)) + 
#  geom_point()

hist(data$occupied_beds)
```

@@

@@

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

@@

Weaknesses and next steps should also be included.

@@
